Resistance to chemotherapy and molecularly targeted therapies is a major
factor in limiting the effectiveness of cancer therapies. In many cases
resistance can be linked to genetic changes in target proteins, either pre-
existing or evolutionarily selected during treatment. Key to overcoming this
challenge is the understanding of the molecular determinants of drug binding.
The key physical parameters determining drug effectiveness are the binding
free energy and the residence time of a ligand. Using molecular simulation we
can gain insights into both of these quantities, which can inform both
stratified or personal treatment regimes and drug development. The level of
sampling required to obtain accurate and reproducible binding affinities and
kinetic information can only efficiently be obtained in a timely fashion
through the use of ensembles of many simulations executed on HPC resources. In
state of the art calculation techniques each simulation may, in fact, consist
of a complex multi-stage workflow. The resulting trajectories reveal in atomic
detail how interactions and protein behaviour change as a result of mutations,
and account for the molecular basis of drug efficacy. There is a need to study
a wide range of cancer drugs and candidate ligands in order to support
personalised clinical decision making based on genome sequencing and drug
discovery, using automated workflows underpinned by ensemble-based high
performance computing methods running at unprecedented scales. To support such
scalable and automated execution of workflows on leadership class resources,
this paper introduces the High-throughput Binding Affinity Calculator (HTBAC).

% HTBAC allows the investigation ....
% ... HTBAC provides the ability to separate the "setting-up" (i.e., defining) of a
% workflow from its "execution".


% which is the integration of the BAC -- Binding Affinity Calculator --
% developed by the Centre for Computational Science at UCL, and RADICAL-
% Cybertools (in particular EnTK). H

% HTBAC represents the state-of-the-art in expressing biomedically
% important workflows for rapid, accurate, precise and reliable free energy
% based binding affinity calculations. RADICAL-Cybertools are a suite of
% functional components that support the interoperable and scalable execution of
% multiple simulations. 

