
It is necessary to move beyond the prevailing paradigm of running individual
MD simulations, which provide irreproducible results and cannot provide
meaningful error bars~\cite{Bhati2017}. Further, the ability to flexibly
scale and adapt ensemble-based protocols to the systems of interest is vital
to produce reliable and accurate results on timescales which make it viable
to influence real world decision making. To meet these goals, we % have
are 
% designed and developed 
designing and developing the high-throughput binding affinity calculator
(HTBAC).

HTBAC employs the RADICAL-Cybertools building blocks for workflow systems
\jhanote{Careful not to imply that HTBAC is a workflow system.} We
% demonstrate 
show how HTBAC \jhanote{check for consistency: HTBAC scales, or
implementation of ESMACS protocol scales?} scales almost perfectly to
hundreds of concurrent pipelines of binding affinity calculations on a
leadership class machine. This permits the rapid time-to-solution that is
\mtnote{I struggle to understand `This permits the rapid time-to-solution
that is'} essentially invariant of the size of candidate ligands as well as
the type and number of protocols concurrently employed. The use of software
abstractions (``building blocks'') future proofs users of HTBAC to evolving
hardware platforms, while providing immediate benefits of scale and support
for a range of workflows. Thus, HTBAC represents an important advance towards
the use of molecular dynamics based free energy calculations to the point
where they can produce actionable results both in the clinic and industrial
drug discovery.

In the short term, the development of HTBAC will allow a significant increase
in the size of study. Much of the literature on MD-based free energy
calculations is limited to a few tens of systems, usually of similar drugs
bound to the same protein target. By facilitating investigations of much
larger datasets, HTBAC also provides a step towards tackling grand challenges
in drug design and precision medicine, where it is necessary to understand
the influences on binding strength for hundreds or thousands of drug-protein
variant combinations. Only in aiming to meet this ambitious goals we will be
able to reveal the limits of existing simulation technology and the
potentials used to approximate the chemistry of the real systems.

\footnotesize \textbf{Software and Data} Ensemble toolkit can be found at
\url{http://radicalensemblemd.readthedocs.io/en/latest/} and is released
under the MIT license. Raw data and scripts to reproduce experiments can be
found at \url{https://github.com/radical-experiments/htbac-experiments.}\mtnote{Should we add a link to HTBAC code base?}
