\subsection{Ensemble Molecular Dynamics Simulations}

The strength of drug binding is determined by a thermodynamic property known
as the binding free energy (or binding affinity). One promising technology for
estimating binding free energies and the influence of protein composition on
them is molecular dynamics (MD). In order to study the influence of mutations
on drug binding atomistically detailed models of the drug and target protein
can be used as the starting point for MD simulations. The chemistry of the
system is encoded in what is known as a potential. \cite{Karplus2002} In the
parameterization of the models each atom is assigned a mass and a charge, with
the chemical bonds between them modelled as springs with varying stiffness.
Using Newtonian mechanics the dynamics of the protein and drug can be tracked
and using the principles of statistical mechanics estimates of thermodynamic
properties obtained from simulations of single particles. The potentials used
in the simulations are completely under the control of the user which allows
the user to manipulate the system in ways which would not be possible in
experiments. A particularly powerful example of this is so called `alchemical'
simulations in which the potential used in the simulation changes from that
representing one system to another during execution — allowing the calculation
of free energy differences between the two systems (such as those induced by a
protein mutation).

MD simulations can reveal how interactions change as a result of mutations,
and account for the molecular basis of drug efficacy. This understanding can
form the basis for structure based drug design as well as helping to target
existing therapies based on protein composition. Major challenges however
exist in correctly capturing the system behaviour. Not only is it necessary
that the approximations made in the potential are accurate enough
representations of the real system chemistry but sufficient sampling of phase
space is also required. 

In order for MD simulations to be used as part of clinical decision support
systems it is necessary that results can be obtained in a timely fashion.
Typically interventions are made on a timescale of a few days or at most a
week. This need for rapid turn around times places additional demands on
simulation protocols which need to be optimised to gain results within a short
turn around time.

Further to the scientific and practical considerations outlined above, in
order for simulations to provide actionable predictions it is vital that
robust and reliable uncertainty estimates are provided alongside all
quantitative results. We have developed a number of free energy calculation
protocols based on the use of ensemble molecular dynamics simulations with the
aim of meeting these requirements \cite{Sadiq2008, Sadiq2010, Wan2017brd4,
Wan2017trk}. Basing these computations on the direct calculation of ensemble
averages facilitates the determination of statistically meaningful results
along with complete control of errors. The consequence of the use of the
ensemble approach is the need to automate the simulation, analysis and data
transfer of a large number of simulations. This computational pattern
necessitates the use of middleware that provides reliable coordination and
distribution mechanisms with low performance overheads.